Evaluation of performances

### 2020-04-12 analysis/eval-performance.Rmd
wflow_publish(knitr_in("analysis/eval-performance.Rmd"), view = FALSE,     verbose = TRUE)

# load drake objects
loadd(
  bm_aggregated_new_buffer2
)
library("xtable")
library("flextable")
library("ggbeeswarm")
library("ggsci")
library("ggrepel")
library("ggpubr")
library("here")
library("mlr")
library("dplyr")
library("forcats")
```

@@

df_tab %>%
  xtable::xtable(
    type = "latex",
    caption = "Single fold performances for learner SVM on the HR dataset without using a filter.",
    label = "tab:svm-single-fold-perf"
  ) %>%
  print(
    file = here::here("docs/00-manuscripts/ieee/performance-svm-single-plot.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL
  )

@@

@@

saveRDS(table1, here("docs/00-manuscripts/presentation/table-perf.rda"))

@@

@@

results_aggr %>%
  ggplot(aes(x = rmse_aggr, y = task.id)) +
  # geom_jitter(aes(color = learner_group), size = 2, width = 0, height = 0.3) +
  # geom_dotplot(aes(fill = learner_group), binaxis="y",
  #                        stackdir="up") +
  geom_beeswarm(groupOnX = FALSE, aes(color = learner_group), size = 3) +
  scale_color_nejm(breaks = sort(levels(results_aggr$learner_group))) +
  labs(x = "RMSE", y = "Task", color = "Learner") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(27, 47)) +
  geom_label_repel(
    # subset data to remove out of bounds values
    data = results_aggr[results_aggr$rmse_aggr < 100, ],
    # from ggbeeswarm, avoid overlapping of points by labels
    position = position_quasirandom(),
    aes(label = paste0(filter, ",", round(rmse_aggr, 2))),
    size = 4,
    min.segment.length = 0.1,
    seed = 123,
    point.padding = 0.5
  ) +
  theme_pubr(base_size = 14) +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 14),
    legend.title = element_text(size = 14),
    axis.text.y = element_text(angle = 45),
    plot.margin = unit(c(6, 6, 6, 0), "pt")
  )
```

>>>>

# load drake objects
# loadd(
#   bm_aggregated_new_buffer2
# )
bm_aggregated_new_buffer2 = readRDS(here::here("temporary-bmr.rda"))
library("xtable")
library("flextable")
library("ggbeeswarm")
library("ggsci")
library("ggrepel")
library("ggpubr")
library("here")
library("mlr")
library("dplyr")
library("forcats")
```

@@

df_tab %>%
  xtable::xtable(
    type = "latex",
    caption = "Test fold performances for learner SVM on the HR dataset without using a filter. For each row, the model was trained on observations from fold all other plots and tested on the observations of the given plot.",
    label = "tab:svm-single-fold-perf"
  ) %>%
  print(
    file = here::here("docs/00-manuscripts/ieee/performance-svm-single-plot.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL
  )

@@

Overall leaderboard across all settings, sorted ascending by performance.

@@

saveRDS(table1, here("docs/00-manuscripts/presentation/table-perf-top-10.rda"))

@@

## (Table) T3 All leaner/filter/task combinations ordered descending by performance.

```{r eval-performance-3, warning=FALSE}
table3 <- df_perf %>%
  group_by(learner.id, task.id, filter) %>%
  slice(which.min(rmse_aggr)) %>%
  dplyr::rename(
    "Model" = learner_group,
    "Learner ID" = learner.id,
    "Task" = task.id,
    "Filter" = filter,
    "RMSE" = rmse_aggr,
    "SE" = se,
  ) %>%
  ungroup() %>%
  mutate(Filter = replace(Filter, is.na(Filter), "No Filter")) %>%
  select(-iter, -`Learner ID`) %>%
  arrange(RMSE)

# save as latex table
table3 %>%
  ungroup() %>%
  arrange(desc(RMSE)) %>%
  slice(1:10) %>%
  xtable(
    type = "latex",
    caption = "Worst 10 results for any task/learner/filter combination, sorted by performance.",
    label = "tab:perf-worst-10"
  ) %>%
  print(
    file = here("docs/00-manuscripts/ieee/performance-worst-10.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL
  )

saveRDS(table3, here("docs/00-manuscripts/presentation/table-perf-worst-10.rda"))

table3 %>%
  ungroup() %>%
  arrange(desc(RMSE)) %>%
  slice(1:10) %>% 
  flextable() %>%
  autofit()
```

@@

results_aggr %>%
  ggplot(aes(x = rmse_aggr, y = task.id)) +
  # geom_jitter(aes(color = learner_group), size = 2, width = 0, height = 0.3) +
  # geom_dotplot(aes(fill = learner_group), binaxis="y",
  #                        stackdir="up") +
  geom_beeswarm(groupOnX = FALSE, aes(color = learner_group), size = 3) +
  scale_color_nejm(breaks = sort(levels(results_aggr$learner_group))) +
  labs(x = "RMSE", y = "Task", color = "Learner") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(27, 47)) +
  geom_label_repel(
    # subset data to remove out of bounds values
    data = results_aggr[results_aggr$rmse_aggr < 100, ],
    # from ggbeeswarm, avoid overlapping of points by labels
    position = position_quasirandom(),
    aes(label = paste0(filter, ",", round(rmse_aggr, 2))),
    size = 4,
    min.segment.length = 0.1,
    seed = 123,
    point.padding = 0.5
  ) +
  theme_pubr(base_size = 14) +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 14),
    axis.text.y = element_text(angle = 45),
    plot.margin = unit(c(6, 6, 6, 0), "pt")
  )
```
